Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-04-17 tese2/evaluation.tex
.

Accordingly, we have used the following formula to calculate the intervals for the expected value of the true average with 95\% confidence:

$[\bar{x}-F^{-1}_{t_{(n-1)}}(1-\alpha/2)\times \frac{s}{\sqrt{n}}, \bar{x}+F^{-1}_{t_{(n-1)}}(1-\alpha/2)\times \frac{s}{\sqrt{n}}]$

Where $\alpha=0.05$, $n$ is the number of samples (which may not coincide with the number of tests due to failed tasks) and $s$ is the sample standard deviation that is given by:

$s=\sqrt{\frac{1}{n-1}\Sigma^{n}_{i=1}(x_i-\bar{x})^2}$

@@

@@

>>>>

Accordingly, we have used the following formula to calculate the intervals for the expected value of the true average with 95\% confidence:
\begin{equation}
[\bar{x}-F^{-1}_{t_{(n-1)}}(1-\alpha/2)\times \frac{s}{\sqrt{n}}, \bar{x}+F^{-1}_{t_{(n-1)}}(1-\alpha/2)\times \frac{s}{\sqrt{n}}]
\end{equation}

Where $\alpha=0.05$, $n$ is the number of samples (which may not coincide with the number of tests due to failed tasks), $\bar{x}$ is the sample mean, $x_i$ is the sample value and $s$ is the sample standard deviation that is given by:
\begin{equation}
s=\sqrt{\frac{1}{n-1}\Sigma^{n}_{i=1}(x_i-\bar{x})^2}
\end{equation}

@@

[COMPARE WITH MINIMAL RESULTS (best clicks, best time, no errors)]

@@

In conclusion, 100\% of our testers though that our solution was an innovation and 92.31\% recommended using our solution.
